Network Data Collection for Artifical Intelligence

### 2020-02-26 paper2/paper2.tex
Added a paragraph about using system call traces for host-based features (previous commit was missing .tex file)

>>>>

A different approach is the use of features derived from raw system call traces. The advantage of system call traces over log files is that they contain only raw information about the interaction between programs and the operating system kernel, whereas log files contain data interpreted by various programs, and potentially include large amounts of irrelevant data. There are multiple methods of analysing system calls. Some only look at the pattern of system calls, while others also look at the arguments passed to these system calls. Also, there is a distinction between syntactic features, which depend only on contiguous patterns of system calls, and semantic features, which additionally consider the meaning of system call arguments or groups of discontiguous system calls. The advantage of the semantic approach is that it is able to counter mimicry attacks, where the payload is modified by the attacker with the aim that the system calls it executes cannot be classified as being malicious \cite{creech2014}.
